\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-07-18 popl-2019-journal-v/paper.tex
[POPLjv] Remove todo
[POPLjv] Add Stelios reference todo
[POPLjv] Rewrite well-formed component description (address suggestion)

% see e-mail discussion: we do not see a good way to implement this TODO.
% \todo[inline]{Dominique: I think it would be less confusing and more in line with the overlay semantics story to not add an extra instruction in Figure~\ref{fig:source-syntax} but rather present it as just a special case of the overlay semantics for the same underlying instructions.}

@@

  Informally, a well-formed component respects Write-XOR-Execute.
  This means that there are no execute capabilities for the data memory and no write capability for the code memory.
  The data memory of a well-formed component respects linearity and it may come with preset data structures.
  It may, however, not contain capabilities for the code memory and sets of seals.
  All the available seals of a component should reside in the code memory.

  As discussed before, we only provide guarantees (LSE and WBCF) for components respecting certain semantic rules (reasonable use of seals).
  Components that do not satisfy these requirements are still allowed in \srccm{}, but (as we will see below) function calls in such components will not behave according to the special \srccm{} semantics that guarantees LSE and WBCF.
  To distinguish trusted components (which satisfy reasonability requirements) from adversarial components (which don't), we make use of a set of trusted addresses $\ta$.
  Any component's code memory must fall entirely within or outside of $\ta$, so every component is either trusted or adversarial.
  Some well-formedness requirements are specific for adversarial and trusted components.
  Well-formed adversarial components cannot have return seals.
  On the other hand, well-formed trusted components can have return seals, but must make return seals available to all its calls in a way that is consistent with \stktokens{}.
  This means that each return seal is only used for one call.

  \todo[inline]{Dominique: The following line appears to explain an arbitrary point about well-formedness: I would explain here that well-formedness imposes a quite rigid structure on well-formed components: a component's code memory may contain only data and sets of seals, while the data memory contains only data, non-sealed memory capabilities to the component's data or code memory (respecting linearity) or sealed memory or code capabilities (to the respective part of the component's memory, sealed with closure seals). A component's exports should be sealed code or data capabilities, sealed with a closure seal.
    Also: perhaps move this before the point about adversarial versus trusted components.
  }
  Finally, well-formed components (adversarial and trusted) can export what corresponds to closures, i.e.,  capabilities for data and code memory sealed with a closure seal.
\end{jversion}

@@

>>>>

% Update: see e-mail discussion: we do not see a good way to implement this.
% Dominique: I think it would be less confusing and more in line with the overlay semantics story to not add an extra instruction in Figure~\ref{fig:source-syntax} but rather present it as just a special case of the overlay semantics for the same underlying instructions.

@@

  The well-formedness judgement imposes a quite rigid structure on well-formed components: a component's code memory may contain only data and sets of seals.
  The data memory may contain only data, memory capabilities to the component's data memory (respecting linearity) or sealed memory capabilities (to the component's data memory, sealed with closure seals).
  This makes a clear separation between code and data memory as neither can contain capabilities for the other.
  The separation of the two kinds of memory means that data structures in data memory can be shared without risking unintentionally leaking a return seals that were indirectly accessible through the data structure.
  Informally, a well-formed component respects Write-XOR-Execute which means that all capabilities for code memory at most has read-execute permission and all capabilities for data memory at most has read-write permission.
  A component's exports should be sealed code or data capabilities, sealed with a closure seal.

  As discussed before, we only provide guarantees (LSE and WBCF) for components respecting certain semantic rules (reasonable use of seals).
  Components that do not satisfy these requirements are still allowed in \srccm{}, but (as we will see below) function calls in such components will not behave according to the special \srccm{} semantics that guarantees LSE and WBCF.
  To distinguish trusted components (which satisfy reasonability requirements) from adversarial components (which don't), we make use of a set of trusted addresses $\ta$.
  Any component's code memory must fall entirely within or outside of $\ta$, so every component is either trusted or adversarial.
  Some well-formedness requirements are specific for adversarial and trusted components.
  Well-formed adversarial components cannot have return seals.
  On the other hand, well-formed trusted components can have return seals, but must make return seals available to all its calls in a way that is consistent with \stktokens{}.
  This means that each return seal is only used for one call.
\end{jversion}

@@

% TODO Relate to Stelios' CSF 2019 paper
